---
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r, include = FALSE}
library(tidyverse)
library(plotly)
library(lubridate)
library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(ggridges)
library(usdata)
library(usmap)
library(ggplot2)
library(patchwork)
library(plotly)
library(leaflet)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE
)

theme_set(theme_bw() + 
          theme(legend.position = "bottom",
                legend.title = element_blank(),
                plot.title = element_text(hjust = 0.5, size = 15),
                plot.subtitle = element_text(hjust = 0.5, size = 12)))
```

```{r, message = FALSE, warning = FALSE}
daily_cases = read_csv("./data/case_daily_trends__united_states.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    date = mdy(case_daily_trends_united_states),
    new_cases = as.double(x2),
    seven_day_ma = as.double(x3)) %>% 
  select(date, new_cases, seven_day_ma) %>% 
  slice(-1:-3) %>% 
  map_df(rev) 
```

*To seek how COVID-19 has influenced our transportation over the past few months, we would like first to understand its progress, and we did it by graphing the daily new cases and deaths over time.*

### Daily Trends in Number of COVID-19 Cases in the United States

```{r, message = FALSE, warning = FALSE}
line.fmt = list(dash="solid", width = 1.5, color= "viridius")
 
daily_cases %>% 
  plot_ly(x = ~date, y = ~new_cases, type = "bar", name = "Daily New Cases") %>% 
  add_lines( x=~date, y = ~seven_day_ma, line=line.fmt, name = "7-Day Moving Average") %>% 
  layout(xaxis = list(title = "Date"), yaxis = list(title = "Daily New Cases"))
```

The plot shows the number of daily new cases of COVID-19 from Jan.22nd to Nov.7th, 2020. We can observe an overall continuously increasing trend starts in the middle of March. Eventually, the number of daily confirmed cases reached 132830 on Nov.6th.

### Daily Trends in Number of COVID-19 Deaths in the United States 

```{r, message = FALSE, warning = FALSE}
daily_deaths = read_csv("./data/death_daily_trends__united_states.csv") %>%
  janitor::clean_names() %>% 
  mutate(
    date = mdy(death_daily_trends_united_states),
    new_deaths = as.double(x2),
    seven_day_ma = as.double(x3)) %>% 
    select(date, new_deaths, seven_day_ma) %>% 
    slice(-1:-3) %>% 
    map_df(rev) 

line.fmt = list(dash="solid", width = 1.5, color= "viridius")
 
daily_deaths %>% 
  plot_ly(x = ~date, y = ~new_deaths, type = "bar", name = "Daily New Deaths") %>% 
  add_lines( x=~date, y = ~seven_day_ma, line=line.fmt, name = "7-Day Moving Average") %>% 
  layout(xaxis = list(title = "Date"), yaxis = list(title = "Daily New Deaths"))
```

The plot shows the number of daily new deaths of COVID-19 from Jan.22nd to Nov.7th, 2020. As seen in this plot, the number of daily new deaths started soaring by the end of March and reaches a peak at 6489 deaths per day on Apr.15th. The number is then observed to decrease until it reaches a plateau at around 1000 deaths per day. 